|

### 2022-01-11 text/ManuscriptDraft.Rmd
Manuscript update

## Study site

@@

The annotation process is described in Mann et al., in prep, but in short: We manually annotated all flowers in the sampled image series using the rectangular bounding box tool in the VIA VGG annotation software. Further, we assigned each individual a unique ID. These annotations constitue our ground truth tracks.

# Automatic tracking

@@

## User parameters

@@

# Evaluating tracking perfomance

@@

We could compare number of points in the overlapping tracks. If one is less than e.g. 10% of the other, we'll remove the small track. If more than 10% we'll remove both?

@@

One way to plot?: Time on x-axis, gt id on y axis, tr id as colour. This will show mismatches.

@@

@@

# Filtering

@@

>>>>

## Study site
Toke, perhaps you can fill in some stuff here.

## The image series
Original time-lapse intervals, explanation and result of sampling scheme and subsequent temporal resolution.

@@

We manually annotated all flowers in the sampled image series using the rectangular bounding box tool in the VIA VGG annotation software. Further, we assigned each individual flower a unique ID. These annotations constitute our ground truth tracks.

## Automatic tracking

@@

@@

## Evaluating tracking perfomance

@@

@@

The results of the filtering algorithm on the three series in which our tracking algorithm did not return perfect results are given in table 2 and the pipeline is visualised in fig. 4. Our filtering method successfully extracted 28 tracked flowers with only a single mismatch from the three series with complex scenes using a fixed value of 350 for eps and fixed values for the tracking parameters (10, 10, 10, for running mean, max disappeared and max distance, respectively).

**Table 2:** Results of the filtering algorithm with an eps value of 350 applied across all three series.

#
![](../figures/FilterScores.png){ width=100% }

#
![](../figures/filtering1.png){ width=100% }
![](../figures/filtering2.png){ width=100% }
![](../figures/filtering3.png){ width=100% }

**Figure 4:** Track filtering pipeline. Row 1, 2, and 3 is NARS-13, NARS-04, and NYAA-04, respectively. First column shows the centroid points in the given series, coloured by the track id from the centroid tracking algorithm. Second column shows the polygons calculated from the tracks. The DBSCAN clustering algorithm with eps = 350 was applied to the centroids of these polygons and the polygons are coloured by cluster id. Third row shows the results of the filtering where all tracks that were not assigned a unique cluster whas been removed.

## Tracking

@@

A paragraph about the ecological perspectives of being able to track the individual flowers (at scale).

@@

## Filtering

@@

We applied a single value for the DBSCAN eps parameter in our tracking algorithm. We note that this value could be finetuned for improved results for the individual series (i.e. more flowers extracted without increased number of mismatches). However, as our goal here was to show that a single conservative value can be applied across series, we do not show those results here.

A point on the fact the these series are complex.
